Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-18 PaperVictor.tex
Revise VIctor's version

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, the 
average reflectance $<$R$>$ of PS-based mirrors is maximized within a wide 
wavelength and angular range, for different porosity contrasts. Optimization is 
performed to maximize the reflectance for minimum  thickness of the structure in the 
visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The 
mirrors are designed using \textit{chirped}-type structures and \textit{stacking} 
sub-mirrors. The chirped structures are found to be more suitable for the Vis range, 
while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication 
and testing of some optimized omnidirectional structures with less than 100 periods has 
been demonstrated.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.

On the other hand, different fabrication techniques have been used to obtain omnidirectional (OD) mirrors that operate on the visible and/or near infrared (Vis-NIR) range of the electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
	para este estilo de citas entre corchetes} reported the fabrication of a 
6-pair TiO$_{2}$/SiO$_{2}$ structure with
an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to 
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs 
layers, to obtain an OD with a band from 710 to 950 nm. 
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, since it can be easily manufactured by 
electrochemical etching of crystalline Si in a hydrofluoric 
acid based electrolyte, to obtain a sponge-like nanostructure composed 
of Si and air. By modulating the supplied current and its application 
time during the electrochemical reaction, it is possible to obtain 
multilayer structures allowing for fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region. 
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band 
with relatively small thickness and refractive index contrast. 
\notaV{Se omite la frase "Specifically, our aim is to maximize the 
	reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
	and angles of incidence $\theta$", la idea general esta en la oracion anterior}

This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
	usa referencias a etiquetas para numerar y referir todo} we develop the
methods used to design and calculate the reflectance spectra of the PS
multilayered structures such as chirped structures and mirror
stacks. In Sec. \ref{s:exp} we provide details about the
fabrication of these structures. In Sec. \ref{s:res} we present the numerical
and experimental results corresponding to our proposed structures and compare
them to previous reports. We obtained significantly large band-widths
with relatively thinner structures than reported before. \notaL{Dejo para resultados y
	conclusiones los detalles de con quién comparamos y qué salió.}
Finally, we discuss our conclusions in Section \ref{s:conc}.

\section{Numerical simulation} \label{s:theory}

\notaV{Nombre de la sección propuesta por Dr. David}
\notaL{Pon etiquetas a todo para poderlo referir}
\notaV{Parrafos reescritos por Dr. David}

In this paper, two techniques are developed to design 
multilayer photonic structures. In the first, the wavelength 
($\lambda _{j}$), at which the $j$-th period of the structure 
is designed, is modulated by an increasing function. This can 
be as simple or complex as you like. The proposed function was used to
optimize $<$R$>$ with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
The other technique for proposing highly reflective structures 
over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each 
sub-mirror the dispersion relation is analyzed.

For the analysis of the propagation of electromagnetic fields 
through multilayer systems, we employ the transfer matrix 
method based on Puente-Díaz et al. formalism \cite{Puente2020}. 
In spite some equivalent formulations have been proposed to 
obtain the optical properties of multilayer systems 
\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
recently developed formalism for the numerically stable 
calculation of the reflectance of large multilayer systems. 
Briefly describing, 
we assume a 1D system with variations along the $z$ direction 
and consider an incident linearly polarized beam of light 
(either TE or TM polarization) that propagates throughout 
the structure. The reflectance and transmittance are given by 
$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
respectively, with \cite{Puente2020}
\begin{equation}
	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2Z_{\zeta
	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $Z_0$ and $Z_s$ are the impedances of the vacuum 
and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is chosen for 
TE polarization while $\beta=\text{Re}Z_{s}/ 
\text{Re}Z_{0}$ for TM polarization. The upper sign 
$-$ in Eq. (\ref{rBloch}) and the subscript 
$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
the case of TE polarization, while the lower sign 
$+$ and the subscript $\zeta =0$ correspond to TM 
polarization. Moreover, sub-index $0$ and $s$ 
refer to the incident and substrate media, respectively.
Furthermore, $M_{ij}$ are the elements
of the transfer matrix which relates
the electromagnetic fields of all interfaces in the structure through

\begin{equation}
\resizebox{\textwidth}{!}{$\displaystyle{
	M=\frac{1}{Z^{+}-Z^{-}} \left( 
	\begin{array}{cc}
		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  & 
		-2iZ^{+}Z^{-}\sin KD \\ 
		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
		iKD\right) 
	\end{array}%
	\right) \text{.}}$}  
\label{MsBloch}
\end{equation}
%}
In this case, $Z^{\pm }$ can be obtained as 
\begin{equation}
	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
\end{equation}%
being 
\begin{equation}
	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
		^{2}}\text{,}  \label{LBloch}
\end{equation}%
where the sign that satisfies the relation $\left\vert \Lambda
_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
system, that is, 
\begin{equation}
	\widetilde{M} = \prod \limits_{j=1}^{N}%
	\begin{bmatrix}
		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\ 
		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
	\end{bmatrix}%
	,  \label{Mcoef}
\end{equation}%
where 
\begin{equation}
	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
\end{equation}%
is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
the wavelength $\lambda $ and 
\begin{equation}
	Q=n_{0}q\sin \theta _{i}  \label{Snell}
\end{equation}%
is the projection of wavevector onto the interfaces, 
which is conserved according to Snell's law, with 
$\theta _{i}$ the angle of incidence. The surface 
impedances are given by $Z_{j}=q/k_{j}$ for TE 
polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for 
TM polarization. The complex refractive index of the porous layers were 
obtained through the Bruggeman's effective medium 
theory, which has been reported to adequately reproduce 
the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.

\section{Experimental details}\label{s:exp}

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$, 
with corresponding porosities of 51\% and 76\%, respectively.
The porosity of the layers was obtained by a previous calibration
curve through a gravimetric technique \cite{Pap2006}. The 
etching rate of PS was obtained by synthetizing single layers under 
similar conditions and measuring their thicknesses through Scanning 
Electron Microscopy (SEM). Absolute reflectivity measurements were 
carried out with a Perkin Elmer Lambda 950 UV/Visible 
spectrophotometer with a variable angle universal reflectance 
accessory (URA) for different incident angles $\theta _{i}=10^{\circ 
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and 
$60^{\circ }$ using non-polarized light. The maximum and minimum 
values of $\theta _{i}$ were constrained by the angular range of the 
equipment accessory URA.

@@

\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j-1}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of periods in the structure and $f(\xi)$ is some smooth function that 
goes from 0 to 1 as its argument goes from surface ($\xi=0$) to the 
substrate ($\xi=1)$. We only consider increasing functions $f$ due to 
the high absorption of PS in the ultraviolet region which decreases in 
the visible and becomes negligible in the near infrared, so, the first 
periods are syntonized in the UV-Vis regions. We consider the 
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =Ax^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize \notaV
{Agregue} in order to maximize the average reflectance. The function
$f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
restricting  $\alpha>0$. The function $f_2$ is an arithmetic averages
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$ \notaL{A ¿no debe ser 1/2 a fuerza, para
que $f_2(1)=1$? \notaV{Si}}. The function $f_{3}$ (Eq. (\ref{F3})) is 
designed so that the first addend dominates near the surface and the 
second addend prevails near the substrate, to allow different behaviors 
at the edges \notaV{Omitted "at UV and IR end"} of the spectrum. 
\notaV{Se replanteo el resto del parrafo} The parameters 
that were optimized to obtain the maximum average reflectance were 
$\alpha$, $\beta$, $A$ and $N_{p}$. The reflectance $R(\lambda, 
\theta)$ of the resulting structures was calculated in two regions of 
the electromagnetic spectrum. The first region was chosen from 350 to 
1400 nm and second one was selected from 400 to 3000 nm, both in the 
angular range of $0^\circ$ to $90^\circ$. Additionally, in the first 
region the minimum design wavelength was optimized and the maximum 
design wavelength was set at 1400 nm, while in the second region the 
wavelengths were set at 850 and 3000 nm, respectively. The 
calculations were carried out using the Perl Data Language (PDL) and 
its interface with the MINUIT \cite{minuit} minimization package. The 
optimized parameters corresponding to a porosity contrast of 51 and 76\% 
are shown in Table \ref{tab:tableA}.

>>>>

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage{braket}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

@@

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, the
average reflectance $\braket{R}$ \notaL{No entiendo por qué insisten
  en no usar tipografía matemática para símbolos como $R$. Los
  símbolos de menor y mayor no corresponden a los de promediar.}. of PS-based mirrors is maximized within a wide
wavelength and angular range for different porosity contrasts. Optimization is
performed to maximize the reflectance for minimum  thickness of the structure in the
visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The
mirrors are designed \notaL{No entiendo para qué haber cambiado el
  modo de activo a pasivo; es mucho mejor el activo.} using \textit{chirped}-type structures and \textit{stacking}
sub-mirrors. The chirped structures are found to be more suitable for the Vis range,
while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication
and testing of some optimized omnidirectional structures with less
than 100 pairs of layers \notaL{Quizás periods no sea correcto, pues
  no son periódicos} has
been demonstrated.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

On the other hand, different fabrication techniques have been used to
obtain omnidirectional (OD) mirrors that operate on the visible and/or
near infrared (Vis-NIR) range of the electromagnetic spectrum. For
example, Chen et al. \cite{Chen1999},
reported the fabrication of a
6-pair TiO$_{2}$/SiO$_{2}$ structure with
an OD band of about 70 nm in the NIR range, employing sol-gel deposition
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs
layers, to obtain an OD with a band from 710 to 950 nm.
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, since it can be easily manufactured by
electrochemical etching crystalline Si in an hydrofluoric
acid based electrolyte, to obtain a sponge-like nanostructure composed
of Si and air. By modulating the supplied current and its application
time during the electrochemical reaction, it is possible to obtain
multilayered structures allowing for the fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region.
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band
with relatively small thickness and refractive index contrast.

This paper is organized as follows. In Sec. \ref{s:theory} we develop the
methods used to design and calculate the reflectance spectra of the PS
multilayered structures such as chirped structures and mirror
stacks. In Sec. \ref{s:exp} we provide details about the
fabrication of these structures. In Sec. \ref{s:res} we present the numerical
and experimental results corresponding to our proposed structures and compare
them to previous reports. We obtained significantly large band-widths
with relatively thinner structures than reported before.
Finally, we discuss our conclusions in Section \ref{s:conc}.

%\section{Numerical simulation} \label{s:theory}
\section{Theory} \label{s:theory}
\notaV{Nombre de la sección propuesta por Dr. David}
\notaL{Estoy en desacuerdo con el título Numerical simulations. Un
  cálculo no es en general una simulación.}
\notaV{Parrafos reescritos por Dr. David}
\notaL{¿Por qué reescribir toda la teoría? ¿Por qué dar tanta teoría?}

We develop two techniques to design
multilayer photonic structures. In the first, the wavelength
($\lambda _{j}$) to which the $j$-th pair of layers is tuned is modulated by
a given function of $j$. Several functions are proposed and their
parameters are optimized to maximize the $\braket{R}$ averaged over
wavelength and angle over a suitable range.
To that end we employed the Minuit module of the Perl Data Language (PDL) \cite{minuit}.
The other technique we employed consisted in stacking
sub-mirrors tuned to different wavelengths, chosen so that their
spectral ranges overlap. For each submirror, the spectral range was
obtained from the dispersion relation of a corresponding periodic
structure.

For the analysis of the propagation of electromagnetic fields
through multilayer systems, we employ a variant of the transfer matrix
method based on the formalism of Puente-Díaz et al. \cite{Puente2020}.
Its advantage over other formally equivalent approaches
\cite{Mochan1987,Ortiz2020,Chavez2020} is that it allows a
numerically stable
calculation of the reflectance even of very large multilayer systems,
even in the presence of absorption.
We assume  the system has  variations only along the $z$ direction
and consider an incident linearly polarized beam of light
(either TE or TM polarization) that propagates throughout
the structure. The reflectance and transmittance are given by
$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
respectively, with \cite{Puente2020}
\begin{equation}
	r=\sigma \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2\zeta}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $Z_0$ and $Z_s$ are the surface impedances of vacuum
and substrate, respectively, $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$,
$\sigma=-1$ and
$\zeta =Z_s$ for
TE polarization, while $\beta=\text{Re}Z_{s}/
\text{Re}Z_{0}$, $\sigma=+1$, and $\zeta =Z_0$ for TM
polarization.
Here, $M_{ij}$ are the elements
of the reconstructed transfer matrix
\begin{equation}
\resizebox{\textwidth}{!}{$\displaystyle{
	M=\frac{1}{Z^{+}-Z^{-}} \left(
	\begin{array}{cc}
		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  &
		-2iZ^{+}Z^{-}\sin KD \\
		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
		iKD\right)
	\end{array}%
	\right) \text{.}}$}
\label{MsBloch}
\end{equation}
which relates the electromagnetic fields at the substrate to those at
the surface,
Here, $Z^{\pm }$ are the surface impedances of the multilayered system
for fields propagating toward the substrate ($+$) or towards vacuum
($-$), and are given by
\begin{equation}
	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
\end{equation}%
where
\begin{equation}
	\Lambda _{-}=\frac{1}{2}\text{Tr}\,\widetilde{M}\pm
        i\sqrt{1-\left( \text{Tr}\,\widetilde{M}/2\right)
		^{2}}\text{,}  \label{LBloch}
\end{equation}%
is chosen to satisfy the inequality $\left\vert \Lambda
_{-}\right\vert >1$, and $\Lambda _{+}=1/\Lambda _{-}$, and Tr denotes
the trace. $\widetilde{M}$ denotes the usual transfer matrix
\begin{equation}
	\widetilde{M} = \prod \limits_{j=1}^{N}%
	\begin{pmatrix}
		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\
		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
	\end{pmatrix}%
	\label{Mcoef}
\end{equation}%
of the multilayered system, where
\begin{equation}
	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
\end{equation}%
is the normal component of the wave vector whithin the $j$-th layer, $Z_{j}$ is
its surface impedance, $Y_{j}=1/Z_{j}$ its surface
admittance, $\epsilon _{j}=n_{j}^{2}$ its permitivity (for simplicity we
assumed all media were nonmagnetic, with permeability $\mu _{i}=1$),
$q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
the wavelength $\lambda $ and
\begin{equation}
	Q=n_{0}q\sin \theta _{i}  \label{Snell}
\end{equation}%
is the projection of wavevector onto the interfaces,
which is conserved according to Snell's law, with
$\theta _{i}$ the angle of incidence. The surface
impedances are given by $Z_{j}=q/k_{j}$ for TE
polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for
TM polarization. The complex refractive index of the porous layers were
obtained through the Bruggeman's effective medium
theory, which has been reported to adequately reproduce
the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
  la referencia.}
\section{Experimental details}\label{s:exp}

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$,
with corresponding porosities of 51\% and 76\%, respectively.
These porosities were obtained through previously obtained calibration
curves using a gravimetric technique \cite{Pap2006}. The
etching rate of PS was obtained by synthetizing single layers under
similar conditions and measuring their thicknesses through Scanning
Electron Microscopy (SEM). Absolute reflectivity measurements were
carried out with a Perkin Elmer Lambda 950 UV/Visible
spectrophotometer with a variable angle universal reflectance
accessory (URA) for different incident angles $\theta _{i}=10^{\circ
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and
$60^{\circ }$ using non-polarized light. The maximum and minimum
values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

\notaL{Aquí quitaron un comentario mío. ¿Ya no es relevante? ¿Ya se
  explicó cómo se hizo el diseño?}
\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure and $f(\xi)$ is some smooth function that
goes from 0 to 1 as its argument goes from surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region which decreases in
the visible and becomes negligible in the near infrared, so, the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =Ax^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize
to maximize the average reflectance $\braket{R}$. The function
$f_{1}$ (Eq. (\ref {F1})) represents simple increasing profiles,
restricting  $\alpha>0$. The function $f_2$ is an arithmetic average
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$. The function $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize $\braket{R}$. The reflectance $R(\lambda,
\theta)$ was calculated for non-polarized light in two regions of
the electromagnetic spectrum. The first region, $\mathcal R_1$,  was chosen from 350 to
1400 nm and second one $\mathcal R_2$ was selected from 400 to 3000 nm, both in the
angular range of $0^\circ$ to $90^\circ$. For $\mathcal R_1$ we took
$\lambda_{\min}$ as a parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both $\lambda_{\min}=850$nm and $\lambda_{\min}=3000$nm. The
calculations were carried out using the Perl Data Language (PDL) and
its interface with the MINUIT \cite{minuit} minimization package. The
optimized parameters corresponding to low and high porosities $p_l=0.51$ and $p_h=0.76$
are shown in Table \ref{tab:tableA}.
